---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library("png")
library("knitr")

```



```{r}

pngs <- read.table("~/txtFiles/pngsFinal.txt")
```
```{r}
i = 1
userOpinion  = vector()
```

```{r}
image_import <- function(image,file_loc){
  readTIFF(paste0(file_loc,"/",image))
}

```




for (i in 1:38){
userOpinion[i] <- readline(prompt = "Is this image bright(b), good(g), dim(d)")
  
}


```{r}
brightnessFirst38 <- read.csv("~/Magneto2020/DataCSV/pngTODOTesting.csv", header = TRUE, stringsAsFactors = FALSE)

above.8 <- vector()
total <- vector()
standard <- vector()
for (i in 1:38){
  name <- brightnessFirst38$ImageName[i]
  path <- brightnessFirst38$ImagePath[i]
  image <- image_import(name,path)
  
  above.8[i] <- length(which(image >= 0.7))
  total[i] <- length(image)
  standard[i] <- above.8[i]/total[i]
}
```

```{r}
xvals = 1:38
df <- data.frame(standard, opinion)
plot(x = xvals, y = df$standard, ylim = c(0, 0.06), col = df$opinion)
legend(x = "topright", legend = paste0("image:", c("bright", "good", "dark")),
fill = c("black", "green", "red"))
```


```{r}
hist(image, breaks = 100)
     #ylim = c(0,4e6))
#hist(temp2, add = TRUE, border = "red", , breaks = 100)
#hist(WithGauss, add = TRUE, border = "blue")
#legend(x = "topright", legend = paste0("image:", c("first", "second", "gauss on 2")),
#fill = c("black", "red", "blue"))
```

